Appendix 6: sdmTMB speed testing methods and model validation description

### 2022-01-08 doc/appendix-validation.Rmd
Update tau_g

sdmTMB_pars$estimate[sdmTMB_pars$term == "tau_G"][1]
sqrt(as.numeric(glmmTMB_varcorr$cond$g))

sdmTMB_pars$estimate[sdmTMB_pars$term == "tau_G"][2]
sqrt(as.numeric(glmmTMB_varcorr$cond$h))

>>>>

sdmTMB_pars$estimate[sdmTMB_pars$term == "sigma_G"][1]
sqrt(as.numeric(glmmTMB_varcorr$cond$g))

sdmTMB_pars$estimate[sdmTMB_pars$term == "sigma_G"][2]
sqrt(as.numeric(glmmTMB_varcorr$cond$h))
